GEE models

### 2017-07-01 doc/manuscript.Rmd
removed lcmm and plsda wording from keywords

- GEE: Generalized estimating equations
- LCMM: Latent curve mixed models
- PLS-DA: Partial least squares regression discriminant analysis
- IGI/IR: Insulinogenic index over HOMA-IR
- ISI: Insulin Sensitivity Index (Matsuda index)
- ISSI-2: Insulin Secretion-Sensitivity Index-2
- ALT: Alanine aminotransferase
- TAG: Triacylglyceride
- PROMISE: Prospective Metabolism and Islet Cell Evaluation Cohort
- QIC: Quasi-Likelihood Information Criterion
- MAQ: Modified Activity Questionnaire
- WC: Waist circumference

>>>>

- GEE: Generalized estimating equations
- IGI/IR: Insulinogenic index over HOMA-IR
- ISI: Insulin Sensitivity Index (Matsuda index)
- ISSI-2: Insulin Secretion-Sensitivity Index-2
- ALT: Alanine aminotransferase
- TAG: Triacylglyceride
- PROMISE: Prospective Metabolism and Islet Cell Evaluation Cohort
- QIC: Quasi-Likelihood Information Criterion
- MAQ: Modified Activity Questionnaire
- WC: Waist circumference
